Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-18 providence/sections/workload.tex
mention quantiles in captions

\subsubsection{Average total ballots.} 
The simplest workload models are a function of just the total number of a ballots sampled.\footnote{Sometimes total \emph{distinct} ballots sampled is used, but for the margins we use in our examples in this section, the difference between total distinct ballots and total ballots is insignificant\cite{arxiv_athena}. It is straightforward to modify the model we discuss here to account for total distinct ballots.} Figure~\ref{fig:avg_bals} shows the average total number of ballots sampled as a function of $p$.
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals.png}
%\includegraphics[width=.5\textwidth]{avg_bals_error_bars_every_three.png}
%\includegraphics[width=.5\textwidth]{avg_bals_errorbars.png}
\includegraphics[width=.5\textwidth]{avg_bals_quantiles.png}
\caption{The average and $0.25$ and $0.75$ quantiles for total number of ballots sampled, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2016 US Presidential election in the US State of Virginia. For sufficiently large $p$ ($p\ge 0.75$), the $0.25$ and $0.75$ quantiles are both equal to the first round size, and this shown by the downward arrows.}
\label{fig:avg_bals}
\end{figure}

Figure~\ref{fig:avg_bals_ratio} provides the same number as a fraction of the \Providence values.
It is straightforward to show that \Providence and both forms of \BRAVO collapse to the same test when each round corresponds to a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), \Providence requires fewer ballots on average. In particular, the savings of \Providence become larger as $p$ increases; for $p=0.95$, EoR \BRAVO and SO \BRAVO require more than $2$ and $1.4$ times as many ballots as \Providence respectively. 
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals_ratio.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
\includegraphics[width=.5\textwidth]{avg_bals_ratio_quantiles.png}
\caption{The total number of ballots sampled on average, as a fraction of those sampled by \Providence, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia.}
\label{fig:avg_bals_ratio}
\end{figure}

@@

\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{with_round_workload.png}
%\includegraphics[width=.5\textwidth]{with_round_workload_errorbars.png}
%\includegraphics[width=.5\textwidth]{round_workload_errorbars.png}
\includegraphics[width=.5\textwidth]{round_workload_quantiles.png}
\caption{For workload parameters $w_b=1$ and $w_r=1000$, this plot shows the expected workload for various values of $p$. Expected workload is found using Equation~\ref{eq:round_workload} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds.}
\label{fig:with_round_workload}
\end{figure}

>>>>

\subsubsection{Average total ballots.} 
The simplest workload models are a function of just the total number of a ballots sampled.\footnote{Sometimes total \emph{distinct} ballots sampled is used, but for the margins we use in our examples in this section, the difference between total distinct ballots and total ballots is insignificant\cite{arxiv_athena}. It is straightforward to modify the model we discuss here to account for total distinct ballots.} Figure~\ref{fig:avg_bals} shows the average total number of ballots sampled as a function of $p$.
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals.png}
%\includegraphics[width=.5\textwidth]{avg_bals_error_bars_every_three.png}
%\includegraphics[width=.5\textwidth]{avg_bals_errorbars.png}
\includegraphics[width=.5\textwidth]{avg_bals_quantiles.png}
\caption{The average total number of ballots sampled, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2016 US Presidential election in the US State of Virginia. Error bars show the $0.25$ and $0.75$ quantiles. For sufficiently large $p$ ($p\ge 0.75$), the $0.25$ and $0.75$ quantiles are both equal to the first round size, and this is shown by the downward arrows.}
\label{fig:avg_bals}
\end{figure}

Figure~\ref{fig:avg_bals_ratio} provides the same number as a fraction of the \Providence values.
It is straightforward to show that \Providence and both forms of \BRAVO collapse to the same test when each round corresponds to a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), \Providence requires fewer ballots on average. In particular, the savings of \Providence become larger as $p$ increases; for $p=0.95$, EoR \BRAVO and SO \BRAVO require more than $2$ and $1.4$ times as many ballots as \Providence respectively. 
\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{avg_bals_ratio.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
%\includegraphics[width=.5\textwidth]{avg_bals_ratio_errorbars.png}
\includegraphics[width=.5\textwidth]{avg_bals_ratio_quantiles.png}
\caption{The total number of ballots sampled on average, as a fraction of those sampled by \Providence, as a function of $p$, the conditional stopping probability used to select each round size, for ballot polling audits of the 2020 US Presidential election in the state of Virginia. The $0.25$ and $0.75$ quantiles are shown as in Figure~\ref{fig:avg_bals}.}
\label{fig:avg_bals_ratio}
\end{figure}

@@

\begin{figure}[h!]
%\includegraphics[width=.5\textwidth]{with_round_workload.png}
%\includegraphics[width=.5\textwidth]{with_round_workload_errorbars.png}
%\includegraphics[width=.5\textwidth]{round_workload_errorbars.png}
\includegraphics[width=.5\textwidth]{round_workload_quantiles.png}
\caption{For workload parameters $w_b=1$ and $w_r=1000$, this plot shows the expected workload for various values of $p$. Expected workload is found using Equation~\ref{eq:round_workload} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds. The $0.25$ and $0.75$ quantiles are shown as in Figure~\ref{fig:avg_bals}.}
\label{fig:with_round_workload}
\end{figure}
